---
title: "web_scraping"
author: "Tanya Bonilla"
date: "10/24/2019"
output:
  pdf_document: default
  html_document: default
---

The library **rvest** will read in a website and then convert it/read it into html with *read_html* function. We dentify the nodes that contain the class number, section number, course title, instructor, and enrollment, and store them in their own variables.
```{r}
suppressMessages(library(rvest))
suppressMessages(library(tidyr))
suppressMessages(library(tidyverse))


sched_url <- "http://ems.csuchico.edu/APSS/schedule/spr2019/CSCI.shtml"
sched_html <- read_html(sched_url)

schedule <- sched_html %>%
             html_nodes(".classrow")

title <- schedule %>%
          html_nodes("td.title") %>%
          html_text()

units <- schedule %>%
          html_nodes("td.units") %>%
          html_text() %>%
          as.integer()

subject <- schedule %>%
            html_nodes("td.subj") %>%
            html_text()
class_num <- schedule %>%
            html_nodes("td.cat_num") %>%
            html_text() %>%
            as.integer()

sect <- schedule %>%
        html_nodes("td.sect") %>%
        html_text() %>%
        as.integer()

instructor <- schedule %>%
              html_nodes("td.Instructor") %>%
              html_text()

enrollment <- schedule %>%
              html_nodes("td.enrtot") %>%
              html_text %>%
              as.integer()
```

We then take the variables and store the data in a tibble.
```{r}
new_sched <- tibble( title = title,
                      units = units,
                      subject = subject,
                      class_num = class_num,
                      sect = sect,
                      instructor = instructor,
                      enrollment = enrollment)
```

Here, we create a function that replicates the previous actions, so that we can easily repeat them with other schedules.
```{r}
read_class_schedule <- function(url) {
  website_html<- read_html(url)
  schedule <- website_html %>%
            html_nodes(".classrow")

  title <- schedule %>% 
            html_nodes("td.title") %>%
            html_text()
  
  units <- schedule %>% 
            html_nodes("td.units") %>%
            html_text() %>%
            as.integer()
  
  subject <- schedule %>%
              html_nodes("td.subj") %>%
              html_text() 
  class_num <- schedule %>%
              html_nodes("td.cat_num") %>%
              html_text() %>%
              as.integer() 
  
  sect <- schedule %>%
          html_nodes("td.sect") %>%
          html_text() %>%
          as.integer()
  
  instructor <- schedule %>%
                html_nodes("td.Instructor") %>%
                html_text()
  
  enrollment <- schedule %>%
                html_nodes("td.enrtot") %>%
                html_text %>%
                as.integer()
  
   tibble(title = title,
                      units = units,
                      subject = subject,
                      class_num = class_num,
                      sect = sect,
                      instructor = instructor,
                      enrollment = enrollment)
}
```

This code chuck calls the function for each of the schedules, and combines them all into a single tibble named **csci_math_table**.
```{r, message=FALSE, warning=FALSE}
cscispring_2019 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2019/CSCI.shtml")
cscispring_2020 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2020/CSCI.shtml")
mathspring_2019 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2020/CSCI.shtml")
mathspring_2020 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2020/CSCI.shtml")

csci_math_table <- rbind(cscispring_2019, cscispring_2020, mathspring_2019, mathspring_2020)
csci_math_table
```